---
title: "Alcohol vs Seat choice"
author: "Angelica Romero"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

##Method
predict alcohol consumption base on where you sit      
alcohol consumer is numerical variable        
where you sit is categorical variable      
     
$H_0$ There is no difference between alcohol consumed and the row you choose to sit in.       
$H_A$ There is a difference between alcohol consumed and the row you choose to sit in.     

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The boxplot shows that people who sit in the back consume more alcohol than people who sit in the middle and front. 

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The table shows that students who sit in the back have a higher mean of 8.56 compared to students who sit in the front with a mean of 1.80 and students who sit in the middle who have a mean of 3.33.  
 
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116 where is less than 0.05 therefore we reject the null hypothesis.

```{r}
plot(TukeyHSD(model1))
```

The tukey test shows us that there is no difference middle-front seats compared to middle-back seats and front-back seats. 

## Conclusions

We conclude that that there is a difference in alcohol consumed and which row you sit in therefore we reject the null hypothesis. The basic box plot shows that the mean of people who sit in the back row is higher than the mean of people who sit in the front row and people who sit in the middle row. With the Tukey test we can see that there is no difference in people who sit in the middle-front row but there is a difference who sit in the middle-back row and the front-back row. With this evidence, it can be proven that there is no difference in alcohol consumer and which row you sit in. 

