---
title: "Alcohol vs Seat choice"
author: "Angelica Romero"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

##Method
predict alcohol consumption base on where you sit      
alcohol consumer is numerical variable        
where you sit is categorical variable      
     
$H_0$ There is no difference between alcohol consumed and the row you choose to sit in.       
$H_A$ There is a difference between alcohol consumed and the row you choose to sit in.     

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The boxplot shows that people who sit in the back consume more alcohol than people who sit in the middle and front. 

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The table shows that students who sit in the back have a higher mean of 8.56 compared to students who sit in the front with a mean of 1.80 and students who sit in the middle who have a mean of 3.33.  
 
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116 where is less than 0.05 therefore we reject the null hypothesis?

```{r}
plot(TukeyHSD(model1))
```

## Conclusions


